---
title: "Analyses of the parity of category systems"
output: html_document
---

Plots and analyses for Kemp, Even or Odd? Symmetry and the size of category systems across languages.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lingtypology)
library(here)
library(tidyverse)
library(patchwork)
library(wcs)
library(glmmTMB)
library(kableExtra)
library(scales)
library(boot)
library(brms)
library(testthat)

mytheme <-  theme_classic(base_size = 10)  +
            theme(strip.background = element_blank()) 

odd_even_cols <- c("#619CFF", "#F8766D")

kinship_classes <- c("siblings", "aunts+uncles", "grandparents", "grandchildren", "nieces+nephews", "cousins")

# treat these cases as unique when including langfamily as random effect
uniques <- c("", "Bookkeeping", "Mixed Language", "Pidgin", "Sign Language", "Speech register",  "Unattested", "Unclassifiable")

# load Glottolog, which will be used to specify language families for mixed models
gl <- glottolog %>% 
  select(language, glottocode, iso, area, affiliation, longitude, latitude) %>% 
  # remove initial parentheses 
  mutate(glottolog_langname= str_replace(language, " \\(.*\\)", "")) %>% 
  mutate(langfamily=affiliation) %>% 
  mutate(langfamily_split= str_split(affiliation, ", ")) %>% 
  mutate(langfamily = map_chr(langfamily_split, 1)) %>% 
  mutate(rownum = row_number()) %>% 
  mutate(langfamily = if_else(langfamily %in% uniques, paste0(langfamily, rownum), langfamily)) %>% 
  select(-language, -langfamily_split, -rownum) 

parity_levels <- c("odd", "even")
```

First set up helper functions for running regressions.

```{r run_regression}

# function for frequentist regression analysis (using glmmTMB)
run_glmmTMB <- function(dstats, domainname) {
  rtype <- "langfamily"
  dstats <- dstats  %>% 
   mutate(parity = factor(parity, levels = parity_levels))
 
  if (domainname %in% paste0("m_", kinship_classes)) {
     rtype <- "--"
     m0 <- glm(parity ~ 0,  data = dstats, family = "binomial", weights = count)
     m1 <- glm(parity ~ 1,  data = dstats, family = "binomial", weights = count)
     coef <- m1$coefficients[1]
     m1conf <- confint(m1)
     lb <- m1conf[1]
     ub <- m1conf[2]
     a <- anova(m1, m0, test = "Chisq")
     pval <- a$`Pr(>Chi)`[2]
  } else if (domainname %in% c("locational (cardinal)") ) {
     rtype <- "--"
     m0 <- glm(parity ~ 0,  data = dstats, family = "binomial")
     m1 <- glm(parity ~ 1,  data = dstats, family = "binomial")
     coef <- m1$coefficients[1]
     m1conf <- confint(m1)
     lb <- m1conf[1]
     ub <- m1conf[2]
     a <- anova(m1, m0, test = "Chisq")
     pval <- a$`Pr(>Chi)`[2]
  } else  {
     lang_count <- dstats %>% 
        group_by(glottocode) %>% 
        mutate(n = n())
     max_lang <- max(lang_count$n) 
     if (max_lang == 1) {
      m0 <- glmmTMB(parity ~ 0 + offset(rep(0, nrow(dstats))) + (1|langfamily),  data = dstats, family = "binomial")
      m1 <- glmmTMB(parity ~ 1 + (1|langfamily), data = dstats, family = "binomial")
    } else {
      rtype <- "lang/langfamily"
      m0 <- glmmTMB(parity ~ 0 + offset(rep(0, nrow(dstats))) + (1|glottocode) + (1|langfamily),  data = dstats, family = "binomial")
      m1 <- glmmTMB(parity ~ 1 + (1|glottocode) + (1|langfamily), data = dstats, family = "binomial")
    }
    coef <- fixef(m1)$cond["(Intercept)"]
    m1conf <- confint(m1)
    lb <- m1conf[1,1]
    ub <- m1conf[1,2]
    
    a <- anova(m1, m0)
    pval <- a$`Pr(>Chisq)`[2]
  }
  
  nlang <- length(unique(dstats$glottocode))
  nsys <- nrow(dstats)
  
  summ <- tibble(
    domain = domainname,
    coefficient = coef,
    p_val = pval,
    lb = lb,
    ub = ub,
    type = rtype,
    nlang = nlang,
    nsys = nsys
  )  
}

# function for Bayesian regression analysis (using brms)
run_brms <- function(dstats, domainname) {
  summ <- tibble(
    domain = domainname,
    coefficient =  0,
    lb = 0,
    ub = 0
  )  
  
  lang_count <- dstats %>% 
    group_by(glottocode) %>% 
    mutate(n = n())
  max_lang <- max(lang_count$n) 
  
  nchain <- 4
  niter <- 3000
  b_con <- list(adapt_delta = 0.95)
  
  dstats <- dstats %>% 
    mutate(parity = parity == "even")
  
  if (domainname == "locational (cardinal)") {
    rtype <- "--"
    m1 <- brm( parity ~ 1, data = dstats, family = bernoulli(), chains = nchain, iter = niter, control = b_con ) 
  }  else if(max_lang == 1 ) {
    rtype <- "langfamily"
    m1 <- brm( parity ~ 1 + (1|langfamily), data = dstats, family = bernoulli(), chains = nchain, iter = niter, control = b_con ) 
  } else {
    rtype <- "lang/langfamily"
    m1 <- brm( parity ~ 1 + (1|glottocode) + (1|langfamily), data = dstats, family = bernoulli(), chains = nchain, iter = niter, control = b_con ) 
  }
    
  brms_tab <- fixef(m1) %>% as_tibble(rownames="NA")
  
  nlang <- length(unique(dstats$glottocode))
  nsys <- nrow(dstats)
  
  summ <- tibble(
    domain = domainname,
    coefficient =  brms_tab$Estimate,
    lb = brms_tab$Q2.5,
    ub = brms_tab$Q97.5,
    type = rtype,
    nlang = nlang,
    nsys = nsys
  )  
}

# run regression analysis for multiple subdomains
run_regression_group <- function(dstats_group, regression_function) {
 dstats_all <- dstats_group %>% 
   group_by(domain) %>% 
   nest() %>% 
   ungroup()
  
  summ <- dstats_all %>% 
    mutate(result = map2(data, domain, regression_function)) %>% 
    select(-domain, -data) %>% 
    unnest(cols = c(result))
}
```

Now run the analyses for each domain in turn

## Deictic day naming and Tense

```{r temporal, cache=TRUE}
tense_data <- read_csv(here("data", "velupillai_tense_data.csv")) %>% 
  rename(size = complexity)
deictic_data <- read_csv(here("data", "tent_deictic_systems.csv")) %>% 
  rename(size = complexity)

make_counts <- function(d) {
  d %>% 
    group_by(size) %>% 
    summarize(count = n(), .groups = "drop") %>% 
    mutate(parity = factor(size %% 2, label= c("even", "odd")))
}  

# drop systems with no tense marking
tense_counts <- make_counts(tense_data) %>% 
  filter(size > 0) %>% 
  mutate(domain = "tense")
  
deictic_counts <- make_counts(deictic_data) %>% mutate(domain = "deictic day names")

all_counts <- bind_rows(deictic_counts, tense_counts)

tense_parity_counts <- tense_counts %>% 
  filter(size > 0) %>% 
  group_by(parity) %>% 
  summarize(count = sum(count), .groups = "drop") %>% 
  mutate(domain = "tense")

deictic_parity_counts <- deictic_counts %>% 
  group_by(parity) %>% 
  summarize(count = sum(count), .groups = "drop") %>% 
  mutate(domain = "deictic day names")

all_parity_counts <- bind_rows(deictic_parity_counts, tense_parity_counts)

tense_stats_data <- tense_data %>% 
  select(gcode, family, size) %>% 
  rename(glottocode = gcode) %>% 
  mutate(rn = row_number()) %>% 
  mutate(family = if_else(family == "Unclassified", paste0(family, rn), family)) %>% 
  select(-rn) %>% 
  filter(size > 0) %>% 
  mutate(parity = factor(size %% 2, label= c("even", "odd"))) %>% 
  left_join(gl, by = "glottocode")

deictic_stats_data <- deictic_data  %>% 
  select(gcode, phylum_family, size) %>% 
  rename(family = phylum_family) %>% 
  mutate(rn = row_number()) %>% 
  mutate(family = if_else(family %in% c("ARTIFICIAL", "ISOLATE", "PIDGINS & CREOLES"), paste0(family, rn), family)) %>% 
  select(-rn) %>% 
  mutate(parity = factor(size %% 2, label= c("even", "odd"))) %>% 
  rename(glottocode = gcode) %>% 
  left_join(gl, by = "glottocode")
    
plot_sizes <- function(counts, parity_counts, ylabel) {
   counts <- counts %>%  
     mutate(parity = factor(parity, levels = parity_levels))
   
   parity_counts <- parity_counts %>%  
     mutate(parity = factor(parity, levels = parity_levels))
  
  # decided not to show systems of size 0 in plot, because they don't contribute to the overall even count. 
  
  size_plot <- counts %>% 
    ggplot(aes(x=size, y = count, fill=parity, color=parity)) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = c("odd" = odd_even_cols[1], "even" = odd_even_cols[2]), drop = FALSE) +
    scale_color_manual(values = c("odd" = odd_even_cols[1], "even" = odd_even_cols[2]), drop = FALSE) +
    ylab('system count') + 
    mytheme +
    theme(legend.position = "none") 
  
  parity_plot <- parity_counts %>% 
    ggplot(aes(x=parity, y = count, fill=parity, color=parity)) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = c("odd" = odd_even_cols[1], "even" = odd_even_cols[2]), drop = FALSE) +
    scale_color_manual(values = c("odd" = odd_even_cols[1], "even" = odd_even_cols[2]), drop = FALSE) +
    ylab('system count') + 
    mytheme +
    theme(legend.position = "none")
  
  double_plot <- size_plot + parity_plot +
    plot_layout(widths = c(2,1)) +
    plot_annotation(tag_levels = c('a'), tag_suffix = ')')
} 

tense_plot <- plot_sizes(tense_counts, tense_parity_counts, 'Tense system count') 
deictic_plot <- plot_sizes(deictic_counts, deictic_parity_counts, 'Temporal deictic system count') 
show(tense_plot)
show(deictic_plot)

deictic_results <- run_glmmTMB(deictic_stats_data, "deictic day names") 
deictic_results_bayes <- run_brms(deictic_stats_data %>% filter(!is.na(glottocode)), "deictic day names") 

tense_results <- run_glmmTMB(tense_stats_data, "tense") 
tense_results_bayes <- run_brms(tense_stats_data, "tense") 

all_results <- bind_rows(deictic_results, tense_results)
all_results_bayes <- bind_rows(deictic_results_bayes, tense_results_bayes)
```         

## Seasons

```{r seasons, cache = TRUE}   
# drop systems with no seasons
seasons_data <- read_csv(here("data", "kemp_seasons.csv")) %>% 
  filter(size > 0) 

seasons_counts <- make_counts(seasons_data) %>% 
  mutate(domain = "seasons")

seasons_parity_counts <- seasons_counts %>% 
  filter(size > 0) %>% 
  group_by(parity) %>% 
  summarize(count = sum(count), .groups = "drop") %>% 
  mutate(domain = "seasons")

seasons_stats_data_orig <- seasons_data %>% 
  rename(glottocode = gcode) %>% 
  left_join(gl, by = "glottocode") %>% 
  select(glottocode, langname, size, langfamily) %>% 
  mutate(parity = factor(size %% 2, label= c("even", "odd"))) 
  
seasons_stats_lcount <- seasons_stats_data_orig %>% 
  group_by(glottocode) %>% 
  mutate(lcount = n())

seasons_mult <- seasons_stats_lcount %>% 
  filter(lcount > 1)
# we have a handful of languages with multiple systems. If all have the same parity ...
expect_equal(length(unique(seasons_mult$parity)), 1)
# it's safe to keep just the first of each 
seasons_stats_data <- seasons_stats_data_orig %>% 
    distinct(glottocode, .keep_all = TRUE)

seasons_plot <- plot_sizes(seasons_counts, seasons_parity_counts, 'Season system count')
show(seasons_plot)

seasons_results <- run_glmmTMB(seasons_stats_data, "seasons") 
seasons_results_bayes <- run_brms(seasons_stats_data, "seasons") 

all_counts <- bind_rows(all_counts, seasons_counts)
all_parity_counts <- bind_rows(all_parity_counts, seasons_parity_counts)
all_results <- bind_rows(all_results, seasons_results)
all_results_bayes <- bind_rows(all_results_bayes, seasons_results_bayes)
```

## Moon Phases

```{r moonphases, cache = TRUE}

moonphases_data <- read_csv(here("data", "kemp_moonphases.csv"))  %>% 
  filter(!is.na(gcode))

moonphases_counts <- make_counts(moonphases_data) %>% 
  mutate(domain = "moon phases")

moonphases_parity_counts <- moonphases_counts %>% 
  group_by(parity) %>% 
  summarize(count = sum(count), .groups = "drop") %>% 
  mutate(domain = "moon phases")

moonphases_plot <- plot_sizes(moonphases_counts, moonphases_parity_counts, 'Moon phases system count')
show(moonphases_plot)

moonphases_stats_data_orig <- moonphases_data %>% 
  rename(glottocode = gcode) %>% 
  left_join(gl, by = "glottocode") %>% 
  select(glottocode, size, langfamily) %>% 
  mutate(parity = factor(size %% 2, label= c("even", "odd"))) 

moonphases_stats_lcount <- moonphases_stats_data_orig %>% 
  group_by(glottocode) %>% 
  mutate(lcount = n())

moonphases_mult <- moonphases_stats_lcount %>% 
  filter(lcount > 1)

# we have a handful of languages with multiple systems. If all have the same parity ...
expect_equal(length(unique(moonphases_mult$parity)), 1)
# it's safe to keep just the first of each 
moonphases_stats_data <- moonphases_stats_data_orig %>% 
    distinct(glottocode, .keep_all = TRUE)
  
moonphases_results <- run_glmmTMB(moonphases_stats_data, "moon phases") 
moonphases_results_bayes <- run_brms(moonphases_stats_data, "moon phases") 

all_counts <- bind_rows(all_counts, moonphases_counts)
all_parity_counts <- bind_rows(all_parity_counts, moonphases_parity_counts)
all_results <- bind_rows(all_results, moonphases_results)
all_results_bayes <- bind_rows(all_results_bayes, moonphases_results_bayes)
```

## Locational systems
```{r locational, cache=TRUE}

# drop compass_relative (one language only), and all types involving vertical/topographic because they were especially hard to code

type_keep <-c("compass_absolute", "sun_only", "wind_only", "wind_and_climate", "climate_weather", "coast_and_wind", "coast_only", "sun_coast_and_river", "river_and_sun", "river_only", "tide", "spiritual_cultural_places_of_significance", "other")

locational_data <- read_csv(here("data", "ozspace_sizes.csv"))  %>% 
  rename(class=type)  %>% 
  filter(class %in% type_keep)

locational_counts <- locational_data %>% 
  group_by(class, size) %>% 
  summarize(count = n(), .groups = "drop") %>% 
  filter(size > 0) %>% 
  mutate(parity = factor(size %% 2, label= c("even", "odd"))) 

locational_parity_counts <- locational_counts %>% 
  group_by(parity, class) %>% 
  summarize(count = sum(count), .groups = "drop")
  
plot_sizes_class <- function(counts, parity_counts) {
  counts <- counts %>%  
    mutate(parity = factor(parity, levels = parity_levels))
   
  parity_counts <- parity_counts %>%  
    mutate(parity = factor(parity, levels = parity_levels))
  
  size_plot <- counts %>% 
    ggplot(aes(x=size, y = count, fill=parity, color=parity)) +
    geom_bar(stat = "identity") +
    theme(legend.position = "none") +
    facet_wrap(~class, scales = "free_y")
  
  parity_plot <- parity_counts %>% 
    ggplot(aes(x=parity, y = count, fill=parity, color=parity)) +
    geom_bar(stat = "identity") +
    theme(legend.position = "none") +
    facet_wrap(~class, scales = "free_y")
  
  double_plot <- size_plot +  parity_plot +
    plot_layout(widths = c(2,1))
} 

locational_plot <- plot_sizes_class(locational_counts, locational_parity_counts)
show(locational_plot)

locational_data_group <- locational_data  %>% 
  mutate(domain= if_else(class == "compass_absolute", "locational (cardinal)", "locational (other)"))
  
locational_counts_group <- locational_data_group %>% 
  group_by(domain, size) %>% 
  summarize(count = n(), .groups = "drop") %>% 
  filter(size > 0) %>% 
  mutate(parity = factor(size %% 2, label= c("even", "odd"))) 

locational_parity_counts_group <- locational_counts_group %>% 
  group_by(parity, domain) %>% 
  summarize(count = sum(count), .groups = "drop")

locational_stats_group_data_full <- locational_data_group %>% 
  select(iso, language, size, domain, gcode_manual) %>% 
  mutate(parity = factor(size %% 2, label= c("even", "odd"))) %>% 
  left_join(gl %>% select(iso, glottocode), by = "iso") %>% 
  select(-iso) %>% 
  mutate(glottocode = if_else(!is.na(gcode_manual), gcode_manual, glottocode)) %>% 
  left_join(gl, by = "glottocode") 

# include at most one cardinal system per glottocode 
locational_stats_group_data <- locational_stats_group_data_full %>% 
    # keep odd-numbered Wajarri cardinal system
    filter(!(language == "Wajarri" & domain == "locational (cardinal)") | size == 3)  %>% 
    mutate(rn = row_number()) %>% 
    mutate(rn = if_else(domain == "locational (cardinal)", 0, rn)) %>% 
    distinct(glottocode, rn, .keep_all = TRUE)

locational_results <- run_regression_group(locational_stats_group_data, run_glmmTMB)
locational_results_bayes <- run_regression_group(locational_stats_group_data, run_brms)

all_counts <- bind_rows(all_counts, locational_counts_group)
all_parity_counts <- bind_rows(all_parity_counts, locational_parity_counts_group)
all_results <- bind_rows(all_results, locational_results)
all_results_bayes <- bind_rows(all_results_bayes, locational_results_bayes)
```

## Kinship

```{r kinship_kinbank, cache = TRUE}
kinship_data <- read_csv(here("data", "kinbank_kinship.csv"))  %>% 
    mutate(
      class = case_match(
      class,
      "parent_siblings" ~ "aunts+uncles",
      "nieces_nephews" ~ "nieces+nephews",
      .default = class 
      )
    ) %>% 
  mutate(domain= factor(class, levels = kinship_classes))  %>% 
  # still needed even though we didn't include concepts like mG and fG for sibling -- some systems (e.g. bann1247) list meB, myB, meZ, myZ, feB, fyB, feZ, fyZ, separately with the same form.
  filter(size > 1) 

kinship_counts <- kinship_data %>% 
  group_by(class, size) %>% 
  summarize(count = n(), .groups = "drop") %>% 
  mutate(parity = factor(size %% 2, label= c("even", "odd"))) 

kinship_parity_counts <- kinship_counts %>% 
  group_by(parity, class) %>% 
  summarize(count = sum(count), .groups = "drop")

show(plot_sizes_class(kinship_counts, kinship_parity_counts))

kinship_stats_data <- kinship_data %>% 
  left_join(gl, by = "glottocode") %>% 
  select(domain, glottocode, size, langfamily) %>% 
  mutate(parity = factor(size %% 2, label= c("even", "odd"))) 

kinship_results <- run_regression_group(kinship_stats_data, run_glmmTMB)
kinship_results_bayes <- run_regression_group(kinship_stats_data, run_brms)

all_counts <- bind_rows(all_counts, kinship_counts %>% rename(domain=class))
all_parity_counts <- bind_rows(all_parity_counts, kinship_parity_counts %>% rename(domain=class))
all_results <- bind_rows(all_results, kinship_results)
all_results_bayes <- bind_rows(all_results_bayes, kinship_results_bayes)
```

## Other domains 

Social classification systems

```{r social}
all_austkin <- c("sections", "subsections", "underspecified sections", "matri-moieties", "patri-moieties", "generational moieties", "matri-semi-moieties", "patri-semi-moieties", "phratries", "totems")

social_categories <- c("sections", "subsections", "underspecified sections", "matri-moieties", "patri-moieties", "generational moieties", "matri-semi-moieties", "patri-semi-moieties")

social_counts <- read_csv(here("data", "austkin_sizes.csv"))  %>% 
  rename(size=NumEntries, class=Category) %>% 
  filter(class %in% social_categories) %>% 
  group_by(ID, Name, Code) %>% 
  summarize(size = max(size), .groups = "drop") %>% 
  # manually fix one entry which seems wrong 
  mutate(size = if_else(Name == "Mayi-Kutuna", 4, size)) %>% 
  group_by(size) %>% 
  summarize(count = n(), .groups = "drop") %>% 
  mutate(parity = factor(size %% 2, label= c("even"))) %>% 
  filter(size > 0)  %>% 
  mutate(domain = "social categories")
  #bind_rows(tibble(size = 1, count = 0, parity = "odd"))

social_parity_counts <- social_counts %>% 
  group_by(parity) %>% 
  summarize(count = sum(count), .groups = "drop")  %>% 
  mutate(domain = "social categories")

social_plot <- plot_sizes(social_counts, social_parity_counts, 'social system count')
show(social_plot)

all_counts <- bind_rows(all_counts, social_counts)
all_parity_counts <- bind_rows(all_parity_counts, social_parity_counts)
```

Color

```{r color, cache = TRUE}
modal_response <- term %>% 
  group_by(lang_nr, chip_nr, term_abb) %>% 
  summarize(count = n(), .groups = "drop_last") %>% 
  mutate(total = sum(count), ratio = count/total) %>% 
  filter(ratio >= 0.6)

color_data <- modal_response %>% 
  group_by(lang_nr) %>% 
  summarize(size = length(unique(term_abb)), .groups = "drop") %>% 
  left_join(lang, by = "lang_nr") %>% 
  rename(iso = "iso_693_3") %>% 
  # handle one case manually
  mutate(iso= if_else(lang_name== "Tarahumara (Western)", "tac", iso)) %>% 
  left_join(gl, by = "iso")  

color_counts <- make_counts(color_data) %>% 
  mutate(domain = "color")

color_parity_counts <- color_counts %>% 
  group_by(parity) %>% 
  summarize(count = sum(count), .groups = "drop") %>% 
  mutate(domain = "color")

color_stats_data <- color_data %>% 
  mutate(parity = factor(size %% 2, label= c("even", "odd")))  

color_results <- run_glmmTMB(color_stats_data, "color") 
color_results_bayes <- run_brms(color_stats_data, "color") 

color_plot <- plot_sizes(color_counts, color_parity_counts, 'color system count') 
show(color_plot)

all_counts <- bind_rows(all_counts, color_counts)
all_parity_counts <- bind_rows(all_parity_counts, color_parity_counts)
all_results <- bind_rows(all_results, color_results)
all_results_bayes <- bind_rows(all_results_bayes, color_results_bayes)
```

Lifeform terms

```{r lifeform, cache = TRUE}
lifeform_data <- read_csv(here("data", "brown_lifeforms.csv"))  

lifeform_counts <- make_counts(lifeform_data) %>% 
  mutate(domain = "life forms")

lifeform_parity_counts <- lifeform_counts %>% 
  filter(size > 0) %>% 
  group_by(parity) %>% 
  summarize(count = sum(count), .groups = "drop") %>% 
  mutate(domain = "life forms")

lifeform_stats_data <- lifeform_data %>% 
  left_join(gl, by = "glottocode") %>% 
  select(glottocode, langname, size, langfamily) %>% 
  mutate(parity = factor(size %% 2, label= c("even", "odd"))) 

lifeform_results <- run_glmmTMB(lifeform_stats_data, "life forms") 
lifeform_results_bayes <- run_brms(lifeform_stats_data, "life forms") 

lifeform_plot <- plot_sizes(lifeform_counts, lifeform_parity_counts, 'lifeform system count') 
show(lifeform_plot)

all_counts <- bind_rows(all_counts, lifeform_counts)
all_parity_counts <- bind_rows(all_parity_counts, lifeform_parity_counts)
all_results <- bind_rows(all_results, lifeform_results)
all_results_bayes <- bind_rows(all_results_bayes, lifeform_results_bayes)
```

## Summary figure and tables

```{r overall, fig.height = 10}

domain_order <- c("deictic day names", "tense", "seasons", "moon phases", "locational (cardinal)",  "siblings", "aunts+uncles", "grandparents", "grandchildren", "nieces+nephews", "cousins", "social categories", "locational (other)", "color", "life forms")

all_counts <- all_counts %>%  
    mutate(parity = factor(parity, levels = parity_levels)) %>% 
    mutate(domain = factor(domain, levels = domain_order))
   
all_parity_counts <- all_parity_counts %>%  
    mutate(parity = factor(parity, levels = parity_levels)) %>% 
    mutate(domain = factor(domain, levels = domain_order))
  
all_size_plot <- all_counts %>% 
    ggplot(aes(x=size, y = count, fill=parity, color=parity)) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = c("odd" = odd_even_cols[1], "even" = odd_even_cols[2])) +
    scale_color_manual(values = c("odd" = odd_even_cols[1], "even" = odd_even_cols[2])) +
    facet_wrap(~domain, ncol=5, scales = "free")  +
    mytheme + 
    theme(legend.position = "none") +
    scale_x_continuous(breaks = breaks_pretty())  +
    scale_y_continuous(breaks = pretty_breaks(4)) 

all_parity_plot <- all_parity_counts %>% 
    ggplot(aes(x=parity, y = count, fill=parity, color=parity)) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = c("odd" = odd_even_cols[1], "even" = odd_even_cols[2])) +
    scale_color_manual(values = c("odd" = odd_even_cols[1], "even" = odd_even_cols[2])) +
    theme(legend.position = "none") +
    facet_wrap(~domain, ncol = 5, scales = "free_y")  +
    mytheme +
    theme(legend.position = "none")  +
    scale_y_continuous(breaks = pretty_breaks(2))

all_double_plot <- all_size_plot /  all_parity_plot +
    plot_annotation(tag_levels = c('a'), tag_suffix = ')') +
    plot_layout(heights= c(3,2)) 
  
# treat social categories as special case
all_means <- all_parity_counts %>% 
  group_by(domain) %>% 
  mutate(coefficient = count/sum(count), lb = coefficient, ub = coefficient, p_val = 0) %>% 
  filter( parity == "even") %>% 
  select(domain, coefficient, p_val, lb, ub) %>% 
  filter( domain %in% c("social categories") )
  
logistic <- function(x) { 1/(1+exp(-x)) }

make_plot_results <- function(results, all_means) {
  all_results_transform <- results %>% 
    mutate(coefficient=logistic(coefficient), lb = logistic(lb), ub = logistic(ub) ) %>% 
    bind_rows(all_means) %>% 
    arrange(coefficient) %>% 
    mutate(predict_col = if_else(domain %in% c("tense", "deictic day names"), odd_even_cols[1], odd_even_cols[2])) %>% 
    mutate(predict_col = if_else(domain %in% c("color", "life forms"), "#808588", predict_col))
}

all_result_bayes_forplot <- make_plot_results(all_results_bayes, all_means)
all_result_freq_forplot <- make_plot_results(all_results, all_means)

plot_bayes <- all_result_bayes_forplot %>% 
  ggplot(aes(x=coefficient, fct_reorder(domain, coefficient))) + 
  geom_vline(xintercept=0.5, color = "lightgray") +
  geom_point(aes(color = predict_col)) +
  geom_errorbarh(aes(xmin = lb, xmax = ub, color = predict_col), height = 0.2) +
  scale_color_identity() +
  xlab("proportion of even systems") +
  ylab("domain") +
  mytheme +
  scale_x_continuous(limits = c(0,1), labels = c("0", "0.25", "0.5", "0.75", "1")) 

all_triple_plot <- free( all_double_plot) / plot_bayes +
    plot_annotation(tag_levels = c('a'), tag_suffix = ')') +
    plot_layout(heights= c(6,2)) 

show(all_triple_plot)

ggsave(here("output", "figures", "results_bayes.pdf"), plot = all_triple_plot, width = 7,height = 8)

plot_freq <- plot_bayes  %+% all_result_freq_forplot

ggsave(here("output", "figures", "results_freq.pdf"), plot = plot_freq, height = 8/3)

all_results %>% 
  kable() %>%  
  kable_styling(full_width = FALSE)

all_results_bayes %>% 
  kable() %>%  
  kable_styling(full_width = FALSE)
```


